Modelling the travel time of transit vehicles in \rt through a GTFS-based road network using GPS vehicle locations

### 2019-08-10 anzjs2018/sections/01_introduction.tex
more grammar

In public transport, \rt information (RTI)---%
most notably estimated times of arrival (ETAs)---%
keeps transport users informed of changes to their commute,
allowing them to plan their journey accordingly.
Previous research has shown that perceived waiting time is less
when arrival time information is available \citep{TCRP_2003b},
but in Auckland, RTI is highly unreliable,
leading to frustration and ultimately deterring public transport users.
Inaccurate ETAs are the primary source of this frustration,
as they fluctuate---sometimes dramatically---over time.
While unpredictable changes to traffic conditions may cause this,
it can equally be due to poor schedule calibration.
Furthermore, buses are shown as \emph{on-time} 
if they are not present in the \rt system and 
the service provider has not manually cancelled them,
in which case ETAs are based solely on scheduled arrival times.
Once the scheduled arrival time has passed,
the service is removed from the \rt board,
leaving passengers unsure as to when---if at all---their bus will show up,
a phenomenon referred to as ``ghost buses'' by transport bloggers.

>>>>

In public transport, \rt information (RTI)---%
most notably estimated times of arrival (ETAs)---%
keeps transport users informed of changes to their commute,
allowing them to plan their journey accordingly.
Previous research has shown that perceived waiting time is less
when arrival time information is available \citep{TCRP_2003b};
however, in Auckland, RTI is highly unreliable,
leading to frustration and ultimately deterring public transport users.
Inaccurate ETAs are the primary source of this frustration,
as they fluctuate---sometimes dramatically---over time.
While unpredictable changes to traffic conditions may cause this,
it can equally be due to poor schedule calibration.
Furthermore, buses are shown as \emph{on-time} 
if they are not present in the \rt system and 
the service provider has not manually cancelled them,
in which case ETAs are based solely on scheduled arrival times.
Once the scheduled arrival time has passed,
the service is removed from the \rt board,
leaving passengers unsure as to when---if at all---their bus will show up,
a phenomenon referred to as ``ghost buses'' by transport bloggers.
